### 2017-05-11 Publications/Original Software Publications/Science of Computer Programming/reply letter/letter.tex
updating reply letter
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

  \end{itemize}
\item Page 4
  \begin{itemize}
  \item if multiple threads perform unsynchronized 90 access to shared-memory locations: to the same memory locations, it is crucial to mention that;

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} Response}
    \end{quote}

@@

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} Response}
    \end{quote}

>>>>

  \end{itemize}
\item Page 4
  \begin{itemize}
  \item if multiple threads perform unsynchronized access to shared-memory locations: to the same memory locations, it is crucial to mention that;

@@

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: To be honest, I didn't get it. Do you think this is correct? Could professor Ricardo Pereira help us answer this question appropriately?}}
    \end{quote}
